### 2019-12-20 README.Rmd
added description and example of zone labels

---
output: github_document
---

@@

>>>>

---
output: github_document
editor_options: 
  chunk_output_type: console
---

@@

The zones are labeled by default in the following way. The rings are labels with capital letters, where A is the centre. The segments are numbers using clock hours, so 12, 3, 6, and 9 for north, east, south, west respectivly.

```{r}
z = zb_zone(x)
tm_shape(z) +
  tm_polygons(col = "circle_id", legend.show = FALSE, palette = "magma") + 
  tm_text("label")
```
